---
title: "Lengths and Enviormental Data"
author: "Ben Frey"
date: "6/22/2021"
output: html_document
---

```{r setup, include=FALSE}
#https://rpubs.com/FlyFrey/qaqclengths
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2); library(mgcv); library(gratia); library(data.table); library(plotly) ;library(dplyr);
library(tibble); library(readr)
lengths <- fread('C:/Users/benba/Documents/GitHub/pier-seine/Data/derived/lengths-edata.csv')
lengths[, yr_fac := as.factor(year)]
lengths[, record_num := as.factor(record_num)]
lengths[, wk := week(date)]
lengths[, length2 := as.factor(length)]

vec <- c(1)
lengths$counts <- vec

gg_qq <- function(x, distribution = "norm", ..., line.estimate = NULL, conf = 0.95,
                    labels = names(x)){
    q.function <- eval(parse(text = paste0("q", distribution)))
    d.function <- eval(parse(text = paste0("d", distribution)))
    x <- na.omit(x)
    ord <- order(x)
    n <- length(x)
    P <- ppoints(length(x))
    df <- data.frame(ord.x = x[ord], z = q.function(P, ...))
    
    if(is.null(line.estimate)){
      Q.x <- quantile(df$ord.x, c(0.25, 0.75))
      Q.z <- q.function(c(0.25, 0.75), ...)
      b <- diff(Q.x)/diff(Q.z)
      coef <- c(Q.x[1] - b * Q.z[1], b)
    } else {
      coef <- coef(line.estimate(ord.x ~ z))
    }
    
    zz <- qnorm(1 - (1 - conf)/2)
    SE <- (coef[2]/d.function(df$z)) * sqrt(P * (1 - P)/n)
    fit.value <- coef[1] + coef[2] * df$z
    df$upper <- fit.value + zz * SE
    df$lower <- fit.value - zz * SE
    
    if(!is.null(labels)){ 
      df$label <- ifelse(df$ord.x > df$upper | df$ord.x < df$lower, labels[ord],"")
    }
    
    p <- ggplot(df, aes(x=z, y=ord.x)) +
      geom_point() + 
      geom_abline(intercept = coef[1], slope = coef[2]) +
      geom_ribbon(aes(ymin = lower, ymax = upper), alpha=0.2) 
    if(!is.null(labels)) p <- p + geom_text( aes(label = label))
    print(p)
    coef
}

outlierReplace = function(dataframe, cols, rows, newValue = NA) {
  if (any(rows)) {
    set(dataframe, rows, cols, newValue)
  }
}
```

## Temperature
### Atlantic Silverside

```{r, echo=FALSE, message=FALSE, warning=FALSE}
a.ss <- lengths[grepl('menidia menidia', scientific)]

a.ss <- a.ss %>% mutate(YOY =
                     case_when(length <= 80 ~ "YOY", 
                               length > 80 ~ "1+")
)#adding YOY threshold

outlierReplace(a.ss, "temp", which(a.ss$temp < 1), NA)
a.ss <- a.ss[!is.na(a.ss$temp),]

h1<-ggplot(data=a.ss  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(temp, -temp), text = paste("Week:", wk,"Temp:", temp, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = temp))+ ggtitle("YOY, temp by week") + scale_color_gradient(low="blue", high="red")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=a.ss  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(temp, -temp), text = paste("Week:", wk,"temp:", temp, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = temp))+ ggtitle("1+, temp by week") + scale_color_gradient(low="blue", high="red")

ggplotly(m1,tooltip = "text")


```

### Atlantic needlefish
```{r echo=FALSE, message=FALSE, warning=FALSE}
need <- lengths[grepl('strongylura', scientific)]

need <- need %>% mutate(YOY =
                     case_when(length < 400 ~ "YOY", 
                               length >= 400 ~ "1+")
) #adding YOY threshold

outlierReplace(need, "temp", which(need$temp < 1), NA)
need <- need[!is.na(need$temp),]

h1<-ggplot(data=need  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(temp, -temp), text = paste("Week:", wk,"Temp:", temp, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = temp, fill = temp))+ ggtitle("YOY, temp by week") + scale_color_gradient(low="blue", high="red") + scale_fill_gradient(low="blue", high="red")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=need  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(temp, -temp), text = paste("Week:", wk,"temp:", temp, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = temp, fill = temp))+ ggtitle("1+, temp by week") + scale_color_gradient(low="blue", high="red") + scale_fill_gradient(low="blue", high="red")

ggplotly(m1,tooltip = "text")

```


### Blue crab
```{r echo=FALSE, message=FALSE, warning=FALSE}
crab <- lengths[grepl('sapidus', scientific)]

crab <- crab %>% mutate(YOY =
                     case_when(length <= 128 ~ "YOY", 
                               length > 128 ~ "1+")
) #adding YOY threshold

outlierReplace(crab, "temp", which(crab$temp < 1), NA)
crab <- crab[!is.na(crab$temp),]

h1<-ggplot(data=crab  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(temp, -temp), text = paste("Week:", wk,"Temp:", temp, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = temp, fill = temp))+ ggtitle("YOY, temp by week") + scale_color_gradient(low="blue", high="red") + scale_fill_gradient(low="blue", high="red")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=crab  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(temp, -temp), text = paste("Week:", wk,"temp:", temp, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = temp, fill = temp))+ ggtitle("1+, temp by week") + scale_color_gradient(low="blue", high="red") + scale_fill_gradient(low="blue", high="red")

ggplotly(m1,tooltip = "text")

```

### Spot
```{r echo=FALSE, message=FALSE, warning=FALSE}
spot <- lengths[grepl('xanthurus', scientific)]

spot <- spot %>% mutate(YOY =
                     case_when(length < 170 ~ "YOY", 
                               length >= 170 ~ "1+")
) #adding YOY threshold

outlierReplace(spot, "temp", which(spot$temp < 1), NA)
spot <- spot[!is.na(spot$temp),]

h1<-ggplot(data=spot  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(temp, -temp), text = paste("Week:", wk,"Temp:", temp, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = temp, fill = temp))+ ggtitle("YOY, temp by week") + scale_color_gradient(low="blue", high="red") + scale_fill_gradient(low="blue", high="red")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=spot  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(temp, -temp), text = paste("Week:", wk,"temp:", temp, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = temp, fill = temp))+ ggtitle("1+, temp by week") + scale_color_gradient(low="blue", high="red") + scale_fill_gradient(low="blue", high="red")

ggplotly(m1,tooltip = "text")
```



### Inland silverside
```{r echo=FALSE, message=FALSE, warning=FALSE}
inland <- lengths[grepl('beryllina', scientific)]

inland <- inland %>% mutate(YOY =
                     case_when(length < 60 ~ "YOY", 
                               length >= 60 ~ "1+")
) #adding YOY threshold

outlierReplace(inland, "temp", which(inland$temp < 1), NA)
inland <- inland[!is.na(inland$temp),]

h1<-ggplot(data=inland  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(temp, -temp), text = paste("Week:", wk,"Temp:", temp, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = temp, fill = temp))+ ggtitle("YOY, temp by week") + scale_color_gradient(low="blue", high="red") + scale_fill_gradient(low="blue", high="red")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=inland  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(temp, -temp), text = paste("Week:", wk,"temp:", temp, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = temp, fill = temp))+ ggtitle("1+, temp by week") + scale_color_gradient(low="blue", high="red") + scale_fill_gradient(low="blue", high="red")

ggplotly(m1,tooltip = "text")
```

### Striped bass
```{r echo=FALSE, message=FALSE, warning=FALSE}
bass <- lengths[grepl('saxatilis', scientific)]

bass <- bass %>% mutate(YOY =
                     case_when(length < 270 ~ "YOY", 
                               length >= 270 ~ "1+")
) #adding YOY threshold

outlierReplace(bass, "temp", which(bass$temp < 1), NA)
bass <- bass[!is.na(bass$temp),]

h1<-ggplot(data=bass  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(temp, -temp), text = paste("Week:", wk,"Temp:", temp, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = temp, fill = temp))+ ggtitle("YOY, temp by week") + scale_color_gradient(low="blue", high="red") + scale_fill_gradient(low="blue", high="red")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=bass  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(temp, -temp), text = paste("Week:", wk,"temp:", temp, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = temp, fill = temp))+ ggtitle("1+, temp by week") + scale_color_gradient(low="blue", high="red") + scale_fill_gradient(low="blue", high="red")

ggplotly(m1,tooltip = "text")
```

### Bluefish
```{r echo=FALSE, message=FALSE, warning=FALSE}
blue <- lengths[grepl('saltatrix', scientific)]

blue <- blue %>% mutate(YOY =
                     case_when(length < 140 ~ "YOY", 
                               length >= 140 ~ "1+")
) #adding YOY threshold

outlierReplace(blue, "temp", which(blue$temp < 1), NA)
blue <- blue[!is.na(blue$temp),]

h1<-ggplot(data=blue  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(temp, -temp), text = paste("Week:", wk,"Temp:", temp, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = temp, fill = temp))+ ggtitle("YOY, temp by week") + scale_color_gradient(low="blue", high="red") + scale_fill_gradient(low="blue", high="red")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=blue  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(temp, -temp), text = paste("Week:", wk,"temp:", temp, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = temp, fill = temp))+ ggtitle("1+, temp by week") + scale_color_gradient(low="blue", high="red") + scale_fill_gradient(low="blue", high="red")

ggplotly(m1,tooltip = "text")
```

### Bay anchovy
```{r echo=FALSE, message=FALSE, warning=FALSE}
ancho <- lengths[grepl('mitchilli', scientific)]
outlierReplace(ancho, "length", which(ancho$length > 110), NA)  
ancho <- ancho %>% mutate(YOY =
                     case_when(length < 60 ~ "YOY", 
                               length >= 60 ~ "1+")
) #adding YOY threshold

outlierReplace(ancho, "temp", which(ancho$temp < 1), NA)
ancho <- ancho[!is.na(ancho$temp),]

h1<-ggplot(data=ancho  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(temp, -temp), text = paste("Week:", wk,"Temp:", temp, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = temp, fill = temp))+ ggtitle("YOY, temp by week") + scale_color_gradient(low="blue", high="red") + scale_fill_gradient(low="blue", high="red")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=ancho  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(temp, -temp), text = paste("Week:", wk,"temp:", temp, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = temp, fill = temp))+ ggtitle("1+, temp by week") + scale_color_gradient(low="blue", high="red") + scale_fill_gradient(low="blue", high="red")

ggplotly(m1,tooltip = "text")
```


### Menhaden
```{r echo=FALSE, message=FALSE, warning=FALSE}
men <- lengths[grepl('brevoortia tyrannus', scientific)]

men <- men %>% mutate(YOY =
                     case_when(length < 170 ~ "YOY", 
                               length >= 170 ~ "1+")
) #adding YOY threshold

outlierReplace(men, "temp", which(men$temp < 1), NA)
men <- men[!is.na(men$temp),]

h1<-ggplot(data=men  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(temp, -temp), text = paste("Week:", wk,"Temp:", temp, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = temp, fill = temp))+ ggtitle("YOY, temp by week") + scale_color_gradient(low="blue", high="red") + scale_fill_gradient(low="blue", high="red")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=men  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(temp, -temp), text = paste("Week:", wk,"temp:", temp, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = temp, fill = temp))+ ggtitle("1+, temp by week") + scale_color_gradient(low="blue", high="red") + scale_fill_gradient(low="blue", high="red")

ggplotly(m1,tooltip = "text")

```


### Gizzard shad
```{r echo=FALSE, message=FALSE, warning=FALSE}
shad <- lengths[grepl('dorosoma cepedianum', scientific)]

shad <- shad %>% mutate(YOY =
                     case_when(length < 180 ~ "YOY", 
                               length >= 180 ~ "1+")
) #adding YOY threshold

outlierReplace(shad, "temp", which(shad$temp < 1), NA)
shad <- shad[!is.na(shad$temp),]

h1<-ggplot(data=shad  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(temp, -temp), text = paste("Week:", wk,"Temp:", temp, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = temp, fill = temp))+ ggtitle("YOY, temp by week") + scale_color_gradient(low="blue", high="red") + scale_fill_gradient(low="blue", high="red")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=shad  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(temp, -temp), text = paste("Week:", wk,"temp:", temp, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = temp, fill = temp))+ ggtitle("1+, temp by week") + scale_color_gradient(low="blue", high="red") + scale_fill_gradient(low="blue", high="red")

ggplotly(m1,tooltip = "text")

```


### White perch
```{r echo=FALSE, message=FALSE, warning=FALSE}
perch <- lengths[grepl('morone americana', scientific)]

perch <- perch %>% mutate(YOY =
                     case_when(length < 93 ~ "YOY", 
                               length >= 93 ~ "1+")
) #adding YOY threshold

outlierReplace(perch, "temp", which(perch$temp < 1), NA)
perch <- perch[!is.na(perch$temp),]

h1<-ggplot(data=perch  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(temp, -temp), text = paste("Week:", wk,"Temp:", temp, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = temp, fill = temp))+ ggtitle("YOY, temp by week") + scale_color_gradient(low="blue", high="red") + scale_fill_gradient(low="blue", high="red")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=perch  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(temp, -temp), text = paste("Week:", wk,"temp:", temp, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = temp, fill = temp))+ ggtitle("1+, temp by week") + scale_color_gradient(low="blue", high="red") + scale_fill_gradient(low="blue", high="red")

ggplotly(m1,tooltip = "text")

```

## Salinity
### Atlantic Silverside

```{r, echo=FALSE, message=FALSE, warning=FALSE}
a.ss <- lengths[grepl('menidia menidia', scientific)]

a.ss <- a.ss %>% mutate(YOY =
                     case_when(length <= 80 ~ "YOY", 
                               length > 80 ~ "1+")
)#adding YOY threshold

outlierReplace(a.ss, "sal", which(a.ss$sal < 1), NA)
a.ss <- a.ss[!is.na(a.ss$sal),]

h1<-ggplot(data=a.ss  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(sal, -sal), text = paste("Week:", wk,"sal:", sal, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = sal))+ ggtitle("YOY, sal by week") + scale_color_gradient(low="blue", high="goldenrod2")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=a.ss  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(sal, -sal), text = paste("Week:", wk,"sal:", sal, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = sal))+ ggtitle("1+, sal by week") + scale_color_gradient(low="blue", high="goldenrod2")

ggplotly(m1,tooltip = "text")


```

### Atlantic needlefish
```{r echo=FALSE, message=FALSE, warning=FALSE}
need <- lengths[grepl('strongylura', scientific)]

need <- need %>% mutate(YOY =
                     case_when(length < 400 ~ "YOY", 
                               length >= 400 ~ "1+")
) #adding YOY threshold

outlierReplace(need, "sal", which(need$sal < 1), NA)
need <- need[!is.na(need$sal),]

h1<-ggplot(data=need  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(sal, -sal), text = paste("Week:", wk,"sal:", sal, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = sal, fill = sal))+ ggtitle("YOY, sal by week") + scale_color_gradient(low="blue", high="goldenrod2") + scale_fill_gradient(low="blue", high="goldenrod2")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=need  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(sal, -sal), text = paste("Week:", wk,"sal:", sal, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = sal, fill = sal))+ ggtitle("1+, sal by week") + scale_color_gradient(low="blue", high="goldenrod2") + scale_fill_gradient(low="blue", high="goldenrod2")

ggplotly(m1,tooltip = "text")

```


### Blue crab
```{r echo=FALSE, message=FALSE, warning=FALSE}
crab <- lengths[grepl('sapidus', scientific)]

crab <- crab %>% mutate(YOY =
                     case_when(length <= 128 ~ "YOY", 
                               length > 128 ~ "1+")
) #adding YOY threshold

outlierReplace(crab, "sal", which(crab$sal < 1), NA)
crab <- crab[!is.na(crab$sal),]

h1<-ggplot(data=crab  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(sal, -sal), text = paste("Week:", wk,"sal:", sal, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = sal, fill = sal))+ ggtitle("YOY, sal by week") + scale_color_gradient(low="blue", high="goldenrod2") + scale_fill_gradient(low="blue", high="goldenrod2")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=crab  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(sal, -sal), text = paste("Week:", wk,"sal:", sal, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = sal, fill = sal))+ ggtitle("1+, sal by week") + scale_color_gradient(low="blue", high="goldenrod2") + scale_fill_gradient(low="blue", high="goldenrod2")

ggplotly(m1,tooltip = "text")

```

### Spot
```{r echo=FALSE, message=FALSE, warning=FALSE}
spot <- lengths[grepl('xanthurus', scientific)]

spot <- spot %>% mutate(YOY =
                     case_when(length < 170 ~ "YOY", 
                               length >= 170 ~ "1+")
) #adding YOY threshold

outlierReplace(spot, "sal", which(spot$sal < 1), NA)
spot <- spot[!is.na(spot$sal),]

h1<-ggplot(data=spot  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(sal, -sal), text = paste("Week:", wk,"sal:", sal, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = sal, fill = sal))+ ggtitle("YOY, sal by week") + scale_color_gradient(low="blue", high="goldenrod2") + scale_fill_gradient(low="blue", high="goldenrod2")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=spot  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(sal, -sal), text = paste("Week:", wk,"sal:", sal, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = sal, fill = sal))+ ggtitle("1+, sal by week") + scale_color_gradient(low="blue", high="goldenrod2") + scale_fill_gradient(low="blue", high="goldenrod2")

ggplotly(m1,tooltip = "text")
```



### Inland silverside
```{r echo=FALSE, message=FALSE, warning=FALSE}
inland <- lengths[grepl('beryllina', scientific)]

inland <- inland %>% mutate(YOY =
                     case_when(length < 60 ~ "YOY", 
                               length >= 60 ~ "1+")
) #adding YOY threshold

outlierReplace(inland, "sal", which(inland$sal < 1), NA)
inland <- inland[!is.na(inland$sal),]

h1<-ggplot(data=inland  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(sal, -sal), text = paste("Week:", wk,"sal:", sal, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = sal, fill = sal))+ ggtitle("YOY, sal by week") + scale_color_gradient(low="blue", high="goldenrod2") + scale_fill_gradient(low="blue", high="goldenrod2")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=inland  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(sal, -sal), text = paste("Week:", wk,"sal:", sal, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = sal, fill = sal))+ ggtitle("1+, sal by week") + scale_color_gradient(low="blue", high="goldenrod2") + scale_fill_gradient(low="blue", high="goldenrod2")

ggplotly(m1,tooltip = "text")
```

### Striped bass
```{r echo=FALSE, message=FALSE, warning=FALSE}
bass <- lengths[grepl('saxatilis', scientific)]

bass <- bass %>% mutate(YOY =
                     case_when(length < 270 ~ "YOY", 
                               length >= 270 ~ "1+")
) #adding YOY threshold

outlierReplace(bass, "sal", which(bass$sal < 1), NA)
bass <- bass[!is.na(bass$sal),]

h1<-ggplot(data=bass  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(sal, -sal), text = paste("Week:", wk,"sal:", sal, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = sal, fill = sal))+ ggtitle("YOY, sal by week") + scale_color_gradient(low="blue", high="goldenrod2") + scale_fill_gradient(low="blue", high="goldenrod2")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=bass  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(sal, -sal), text = paste("Week:", wk,"sal:", sal, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = sal, fill = sal))+ ggtitle("1+, sal by week") + scale_color_gradient(low="blue", high="goldenrod2") + scale_fill_gradient(low="blue", high="goldenrod2")

ggplotly(m1,tooltip = "text")
```

### Bluefish
```{r echo=FALSE, message=FALSE, warning=FALSE}
blue <- lengths[grepl('saltatrix', scientific)]

blue <- blue %>% mutate(YOY =
                     case_when(length < 140 ~ "YOY", 
                               length >= 140 ~ "1+")
) #adding YOY threshold

outlierReplace(blue, "sal", which(blue$sal < 1), NA)
blue <- blue[!is.na(blue$sal),]

h1<-ggplot(data=blue  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(sal, -sal), text = paste("Week:", wk,"sal:", sal, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = sal, fill = sal))+ ggtitle("YOY, sal by week") + scale_color_gradient(low="blue", high="goldenrod2") + scale_fill_gradient(low="blue", high="goldenrod2")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=blue  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(sal, -sal), text = paste("Week:", wk,"sal:", sal, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = sal, fill = sal))+ ggtitle("1+, sal by week") + scale_color_gradient(low="blue", high="goldenrod2") + scale_fill_gradient(low="blue", high="goldenrod2")

ggplotly(m1,tooltip = "text")
```

### Bay anchovy
```{r echo=FALSE, message=FALSE, warning=FALSE}
ancho <- lengths[grepl('mitchilli', scientific)]
outlierReplace(ancho, "length", which(ancho$length > 110), NA)  
ancho <- ancho %>% mutate(YOY =
                     case_when(length < 60 ~ "YOY", 
                               length >= 60 ~ "1+")
) #adding YOY threshold

outlierReplace(ancho, "sal", which(ancho$sal < 1), NA)
ancho <- ancho[!is.na(ancho$sal),]

h1<-ggplot(data=ancho  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(sal, -sal), text = paste("Week:", wk,"sal:", sal, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = sal, fill = sal))+ ggtitle("YOY, sal by week") + scale_color_gradient(low="blue", high="goldenrod2") + scale_fill_gradient(low="blue", high="goldenrod2")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=ancho  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(sal, -sal), text = paste("Week:", wk,"sal:", sal, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = sal, fill = sal))+ ggtitle("1+, sal by week") + scale_color_gradient(low="blue", high="goldenrod2") + scale_fill_gradient(low="blue", high="goldenrod2")

ggplotly(m1,tooltip = "text")
```


### Menhaden
```{r echo=FALSE, message=FALSE, warning=FALSE}
men <- lengths[grepl('brevoortia tyrannus', scientific)]

men <- men %>% mutate(YOY =
                     case_when(length < 170 ~ "YOY", 
                               length >= 170 ~ "1+")
) #adding YOY threshold

outlierReplace(men, "sal", which(men$sal < 1), NA)
men <- men[!is.na(men$sal),]

h1<-ggplot(data=men  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(sal, -sal), text = paste("Week:", wk,"sal:", sal, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = sal, fill = sal))+ ggtitle("YOY, sal by week") + scale_color_gradient(low="blue", high="goldenrod2") + scale_fill_gradient(low="blue", high="goldenrod2")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=men  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(sal, -sal), text = paste("Week:", wk,"sal:", sal, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = sal, fill = sal))+ ggtitle("1+, sal by week") + scale_color_gradient(low="blue", high="goldenrod2") + scale_fill_gradient(low="blue", high="goldenrod2")

ggplotly(m1,tooltip = "text")

```


### Gizzard shad
```{r echo=FALSE, message=FALSE, warning=FALSE}
shad <- lengths[grepl('dorosoma cepedianum', scientific)]

shad <- shad %>% mutate(YOY =
                     case_when(length < 180 ~ "YOY", 
                               length >= 180 ~ "1+")
) #adding YOY threshold

outlierReplace(shad, "sal", which(shad$sal < 1), NA)
shad <- shad[!is.na(shad$sal),]

h1<-ggplot(data=shad  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(sal, -sal), text = paste("Week:", wk,"sal:", sal, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = sal, fill = sal))+ ggtitle("YOY, sal by week") + scale_color_gradient(low="blue", high="goldenrod2") + scale_fill_gradient(low="blue", high="goldenrod2")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=shad  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(sal, -sal), text = paste("Week:", wk,"sal:", sal, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = sal, fill = sal))+ ggtitle("1+, sal by week") + scale_color_gradient(low="blue", high="goldenrod2") + scale_fill_gradient(low="blue", high="goldenrod2")

ggplotly(m1,tooltip = "text")

```


### White perch
```{r echo=FALSE, message=FALSE, warning=FALSE}
perch <- lengths[grepl('morone americana', scientific)]

perch <- perch %>% mutate(YOY =
                     case_when(length < 93 ~ "YOY", 
                               length >= 93 ~ "1+")
) #adding YOY threshold

outlierReplace(perch, "sal", which(perch$sal < 1), NA)
perch <- perch[!is.na(perch$sal),]

h1<-ggplot(data=perch  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(sal, -sal), text = paste("Week:", wk,"sal:", sal, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = sal, fill = sal))+ ggtitle("YOY, sal by week") + scale_color_gradient(low="blue", high="goldenrod2") + scale_fill_gradient(low="blue", high="goldenrod2")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=perch  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(sal, -sal), text = paste("Week:", wk,"sal:", sal, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = sal, fill = sal))+ ggtitle("1+, sal by week") + scale_color_gradient(low="blue", high="goldenrod2") + scale_fill_gradient(low="blue", high="goldenrod2")

ggplotly(m1,tooltip = "text")

```


## Dissolved Oxygen
### Atlantic Silverside

```{r, echo=FALSE, message=FALSE, warning=FALSE}
a.ss <- lengths[grepl('menidia menidia', scientific)]

a.ss <- a.ss %>% mutate(YOY =
                     case_when(length <= 80 ~ "YOY", 
                               length > 80 ~ "1+")
)#adding YOY threshold

outlierReplace(a.ss, "DO", which(a.ss$DO < 1), NA)
a.ss <- a.ss[!is.na(a.ss$DO),]

h1<-ggplot(data=a.ss  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(DO, -DO), text = paste("Week:", wk,"DO:", DO, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = DO))+ ggtitle("YOY, DO by week") + scale_color_gradient(low="red", high="limegreen")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=a.ss  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(DO, -DO), text = paste("Week:", wk,"DO:", DO, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = DO))+ ggtitle("1+, DO by week") + scale_color_gradient(low="red", high="limegreen")

ggplotly(m1,tooltip = "text")


```

### Atlantic needlefish
```{r echo=FALSE, message=FALSE, warning=FALSE}
need <- lengths[grepl('strongylura', scientific)]

need <- need %>% mutate(YOY =
                     case_when(length < 400 ~ "YOY", 
                               length >= 400 ~ "1+")
) #adding YOY threshold

outlierReplace(need, "DO", which(need$DO < 1), NA)
need <- need[!is.na(need$DO),]

h1<-ggplot(data=need  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(DO, -DO), text = paste("Week:", wk,"DO:", DO, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = DO, fill = DO))+ ggtitle("YOY, DO by week") + scale_color_gradient(low="red", high="limegreen") + scale_fill_gradient(low="red", high="limegreen")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=need  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(DO, -DO), text = paste("Week:", wk,"DO:", DO, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = DO, fill = DO))+ ggtitle("1+, DO by week") + scale_color_gradient(low="red", high="limegreen") + scale_fill_gradient(low="red", high="limegreen")

ggplotly(m1,tooltip = "text")

```


### Blue crab
```{r echo=FALSE, message=FALSE, warning=FALSE}
crab <- lengths[grepl('sapidus', scientific)]

crab <- crab %>% mutate(YOY =
                     case_when(length <= 128 ~ "YOY", 
                               length > 128 ~ "1+")
) #adding YOY threshold

outlierReplace(crab, "DO", which(crab$DO < 1), NA)
crab <- crab[!is.na(crab$DO),]

h1<-ggplot(data=crab  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(DO, -DO), text = paste("Week:", wk,"DO:", DO, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = DO, fill = DO))+ ggtitle("YOY, DO by week") + scale_color_gradient(low="red", high="limegreen") + scale_fill_gradient(low="red", high="limegreen")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=crab  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(DO, -DO), text = paste("Week:", wk,"DO:", DO, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = DO, fill = DO))+ ggtitle("1+, DO by week") + scale_color_gradient(low="red", high="limegreen") + scale_fill_gradient(low="red", high="limegreen")

ggplotly(m1,tooltip = "text")

```

### Spot
```{r echo=FALSE, message=FALSE, warning=FALSE}
spot <- lengths[grepl('xanthurus', scientific)]

spot <- spot %>% mutate(YOY =
                     case_when(length < 170 ~ "YOY", 
                               length >= 170 ~ "1+")
) #adding YOY threshold

outlierReplace(spot, "DO", which(spot$DO < 1), NA)
spot <- spot[!is.na(spot$DO),]

h1<-ggplot(data=spot  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(DO, -DO), text = paste("Week:", wk,"DO:", DO, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = DO, fill = DO))+ ggtitle("YOY, DO by week") + scale_color_gradient(low="red", high="limegreen") + scale_fill_gradient(low="red", high="limegreen")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=spot  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(DO, -DO), text = paste("Week:", wk,"DO:", DO, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = DO, fill = DO))+ ggtitle("1+, DO by week") + scale_color_gradient(low="red", high="limegreen") + scale_fill_gradient(low="red", high="limegreen")

ggplotly(m1,tooltip = "text")
```



### Inland silverside
```{r echo=FALSE, message=FALSE, warning=FALSE}
inland <- lengths[grepl('beryllina', scientific)]

inland <- inland %>% mutate(YOY =
                     case_when(length < 60 ~ "YOY", 
                               length >= 60 ~ "1+")
) #adding YOY threshold

outlierReplace(inland, "DO", which(inland$DO < 1), NA)
inland <- inland[!is.na(inland$DO),]

h1<-ggplot(data=inland  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(DO, -DO), text = paste("Week:", wk,"DO:", DO, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = DO, fill = DO))+ ggtitle("YOY, DO by week") + scale_color_gradient(low="red", high="limegreen") + scale_fill_gradient(low="red", high="limegreen")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=inland  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(DO, -DO), text = paste("Week:", wk,"DO:", DO, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = DO, fill = DO))+ ggtitle("1+, DO by week") + scale_color_gradient(low="red", high="limegreen") + scale_fill_gradient(low="red", high="limegreen")

ggplotly(m1,tooltip = "text")
```

### Striped bass
```{r echo=FALSE, message=FALSE, warning=FALSE}
bass <- lengths[grepl('saxatilis', scientific)]

bass <- bass %>% mutate(YOY =
                     case_when(length < 270 ~ "YOY", 
                               length >= 270 ~ "1+")
) #adding YOY threshold

outlierReplace(bass, "DO", which(bass$DO < 1), NA)
bass <- bass[!is.na(bass$DO),]

h1<-ggplot(data=bass  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(DO, -DO), text = paste("Week:", wk,"DO:", DO, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = DO, fill = DO))+ ggtitle("YOY, DO by week") + scale_color_gradient(low="red", high="limegreen") + scale_fill_gradient(low="red", high="limegreen")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=bass  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(DO, -DO), text = paste("Week:", wk,"DO:", DO, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = DO, fill = DO))+ ggtitle("1+, DO by week") + scale_color_gradient(low="red", high="limegreen") + scale_fill_gradient(low="red", high="limegreen")

ggplotly(m1,tooltip = "text")
```

### Bluefish
```{r echo=FALSE, message=FALSE, warning=FALSE}
blue <- lengths[grepl('saltatrix', scientific)]

blue <- blue %>% mutate(YOY =
                     case_when(length < 140 ~ "YOY", 
                               length >= 140 ~ "1+")
) #adding YOY threshold

outlierReplace(blue, "DO", which(blue$DO < 1), NA)
blue <- blue[!is.na(blue$DO),]

h1<-ggplot(data=blue  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(DO, -DO), text = paste("Week:", wk,"DO:", DO, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = DO, fill = DO))+ ggtitle("YOY, DO by week") + scale_color_gradient(low="red", high="limegreen") + scale_fill_gradient(low="red", high="limegreen")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=blue  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(DO, -DO), text = paste("Week:", wk,"DO:", DO, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = DO, fill = DO))+ ggtitle("1+, DO by week") + scale_color_gradient(low="red", high="limegreen") + scale_fill_gradient(low="red", high="limegreen")

ggplotly(m1,tooltip = "text")
```

### Bay anchovy
```{r echo=FALSE, message=FALSE, warning=FALSE}
ancho <- lengths[grepl('mitchilli', scientific)]
outlierReplace(ancho, "length", which(ancho$length > 110), NA)  
ancho <- ancho %>% mutate(YOY =
                     case_when(length < 60 ~ "YOY", 
                               length >= 60 ~ "1+")
) #adding YOY threshold

outlierReplace(ancho, "DO", which(ancho$DO < 1), NA)
ancho <- ancho[!is.na(ancho$DO),]

h1<-ggplot(data=ancho  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(DO, -DO), text = paste("Week:", wk,"DO:", DO, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = DO, fill = DO))+ ggtitle("YOY, DO by week") + scale_color_gradient(low="red", high="limegreen") + scale_fill_gradient(low="red", high="limegreen")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=ancho  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(DO, -DO), text = paste("Week:", wk,"DO:", DO, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = DO, fill = DO))+ ggtitle("1+, DO by week") + scale_color_gradient(low="red", high="limegreen") + scale_fill_gradient(low="red", high="limegreen")

ggplotly(m1,tooltip = "text")
```


### Menhaden
```{r echo=FALSE, message=FALSE, warning=FALSE}
men <- lengths[grepl('brevoortia tyrannus', scientific)]

men <- men %>% mutate(YOY =
                     case_when(length < 170 ~ "YOY", 
                               length >= 170 ~ "1+")
) #adding YOY threshold

outlierReplace(men, "DO", which(men$DO < 1), NA)
men <- men[!is.na(men$DO),]

h1<-ggplot(data=men  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(DO, -DO), text = paste("Week:", wk,"DO:", DO, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = DO, fill = DO))+ ggtitle("YOY, DO by week") + scale_color_gradient(low="red", high="limegreen") + scale_fill_gradient(low="red", high="limegreen")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=men  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(DO, -DO), text = paste("Week:", wk,"DO:", DO, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = DO, fill = DO))+ ggtitle("1+, DO by week") + scale_color_gradient(low="red", high="limegreen") + scale_fill_gradient(low="red", high="limegreen")

ggplotly(m1,tooltip = "text")

```


### Gizzard shad
```{r echo=FALSE, message=FALSE, warning=FALSE}
shad <- lengths[grepl('dorosoma cepedianum', scientific)]

shad <- shad %>% mutate(YOY =
                     case_when(length < 180 ~ "YOY", 
                               length >= 180 ~ "1+")
) #adding YOY threshold

outlierReplace(shad, "DO", which(shad$DO < 1), NA)
shad <- shad[!is.na(shad$DO),]

h1<-ggplot(data=shad  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(DO, -DO), text = paste("Week:", wk,"DO:", DO, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = DO, fill = DO))+ ggtitle("YOY, DO by week") + scale_color_gradient(low="red", high="limegreen") + scale_fill_gradient(low="red", high="limegreen")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=shad  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(DO, -DO), text = paste("Week:", wk,"DO:", DO, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = DO, fill = DO))+ ggtitle("1+, DO by week") + scale_color_gradient(low="red", high="limegreen") + scale_fill_gradient(low="red", high="limegreen")

ggplotly(m1,tooltip = "text")

```


### White perch
```{r echo=FALSE, message=FALSE, warning=FALSE}
perch <- lengths[grepl('morone americana', scientific)]

perch <- perch %>% mutate(YOY =
                     case_when(length < 93 ~ "YOY", 
                               length >= 93 ~ "1+")
) #adding YOY threshold

outlierReplace(perch, "DO", which(perch$DO < 1), NA)
perch <- perch[!is.na(perch$DO),]

h1<-ggplot(data=perch  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(DO, -DO), text = paste("Week:", wk,"DO:", DO, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(color = DO, fill = DO))+ ggtitle("YOY, DO by week") + scale_color_gradient(low="red", high="limegreen") + scale_fill_gradient(low="red", high="limegreen")

ggplotly(h1,tooltip = "text")

m1<-ggplot(data=perch  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(DO, -DO), text = paste("Week:", wk,"DO:", DO, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes( color = DO, fill = DO))+ ggtitle("1+, DO by week") + scale_color_gradient(low="red", high="limegreen") + scale_fill_gradient(low="red", high="limegreen")

ggplotly(m1,tooltip = "text")

```
