---
title: "Seine Data, YOY Seperation Organized Length By Week"
author: "Ben Frey"
date: "5/26/2021"
output: html_document
---

```{r setup, include=FALSE}
#https://rpubs.com/FlyFrey/qaqclengths
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2); library(mgcv); library(gratia); library(data.table); library(plotly) ;library(dplyr);
library(tibble); library(readr)
lengths <- fread('C:/Users/ben/Documents/GitHub/pier-seine/Data/derived/lengths2.csv')
lengths[, yr_fac := as.factor(year)]
lengths[, record_num := as.factor(record_num)]
lengths[, wk := week(date)]
lengths[, length2 := as.factor(length)]

vec <- c(1)
lengths$counts <- vec

gg_qq <- function(x, distribution = "norm", ..., line.estimate = NULL, conf = 0.95,
                    labels = names(x)){
    q.function <- eval(parse(text = paste0("q", distribution)))
    d.function <- eval(parse(text = paste0("d", distribution)))
    x <- na.omit(x)
    ord <- order(x)
    n <- length(x)
    P <- ppoints(length(x))
    df <- data.frame(ord.x = x[ord], z = q.function(P, ...))
    
    if(is.null(line.estimate)){
      Q.x <- quantile(df$ord.x, c(0.25, 0.75))
      Q.z <- q.function(c(0.25, 0.75), ...)
      b <- diff(Q.x)/diff(Q.z)
      coef <- c(Q.x[1] - b * Q.z[1], b)
    } else {
      coef <- coef(line.estimate(ord.x ~ z))
    }
    
    zz <- qnorm(1 - (1 - conf)/2)
    SE <- (coef[2]/d.function(df$z)) * sqrt(P * (1 - P)/n)
    fit.value <- coef[1] + coef[2] * df$z
    df$upper <- fit.value + zz * SE
    df$lower <- fit.value - zz * SE
    
    if(!is.null(labels)){ 
      df$label <- ifelse(df$ord.x > df$upper | df$ord.x < df$lower, labels[ord],"")
    }
    
    p <- ggplot(df, aes(x=z, y=ord.x)) +
      geom_point() + 
      geom_abline(intercept = coef[1], slope = coef[2]) +
      geom_ribbon(aes(ymin = lower, ymax = upper), alpha=0.2) 
    if(!is.null(labels)) p <- p + geom_text( aes(label = label))
    print(p)
    coef
}

outlierReplace = function(dataframe, cols, rows, newValue = NA) {
  if (any(rows)) {
    set(dataframe, rows, cols, newValue)
  }
}
```


## QA/QC lengths
### Atlantic Silversides

```{r ASS, echo=FALSE, message=FALSE, warning=FALSE}
a.ss <- lengths[grepl('menidia menidia', scientific)]

a.ss <- a.ss %>% mutate(YOY =
                     case_when(length <= 80 ~ "YOY", 
                               length > 80 ~ "1+")
)#adding YOY threshold

#scale_fill_manual(breaks = c(….))
#scale_fill_manual(breaks = c(seq(50, 100, 10), 500))… I think
#Double gradient

#h1<-ggplot(data=a.ss, aes(x=wk, y=counts, fill = length, color = length,order = reorder(length2, -length), text = paste("Week:", wk,"Length:", length, "Year:", year), show.legend=T)) +geom_bar(stat="identity")+ ggtitle("Length by week") #+ facet_grid(YOY ~ .)
#ggplotly(h1,tooltip = "text")

h1<-ggplot(data=a.ss  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(length2, -length), text = paste("Week:", wk,"Length:", length, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(fill = length, color = length))+ ggtitle("YOY, Length by week") 
ggplotly(h1,tooltip = "text")

m1<-ggplot(data=a.ss  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(length2, -length), text = paste("Week:", wk,"Length:", length, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(fill = length, color = length))+ ggtitle("1+, Length by week") 

ggplotly(m1,tooltip = "text")



```

Background suggests Atlantic silversides are "No bigger than max lengths of 180mm" with YOY max length around 80mm. Outliers Removed > 180.

### Atlantic needlefish
```{r echo=FALSE, message=FALSE, warning=FALSE}
need <- lengths[grepl('strongylura', scientific)]

need <- need %>% mutate(YOY =
                     case_when(length < 400 ~ "YOY", 
                               length >= 400 ~ "1+")
) #adding YOY threshold

h2<-ggplot(data=need  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(length2, -length), text = paste("Week:", wk,"Length:", length, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(fill = length, color = length))+ ggtitle("YOY, Length by week") 

ggplotly(h2,tooltip = "text")

m2<-ggplot(data=need  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(length2, -length), text = paste("Week:", wk,"Length:", length, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(fill = length, color = length))+ ggtitle("1+, Length by week") 

ggplotly(m2,tooltip = "text")



```
Recorded Max length Needlefish : 1110 mm TL with YOY max length around 190-400mm

### Blue crab
```{r echo=FALSE, message=FALSE, warning=FALSE}
crab <- lengths[grepl('sapidus', scientific)]

crab <- crab %>% mutate(YOY =
                     case_when(length <= 128 ~ "YOY", 
                               length > 128 ~ "1+")
) #adding YOY threshold

h3<-ggplot(data=crab  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(length2, -length), text = paste("Week:", wk,"Length:", length, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(fill = length, color = length))+ ggtitle("YOY, Length by week") 

ggplotly(h3,tooltip = "text")

m3<-ggplot(data=crab  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(length2, -length), text = paste("Week:", wk,"Length:", length, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(fill = length, color = length))+ ggtitle("1+, Length by week") 

ggplotly(m3,tooltip = "text")
```
No joy with Blue Crab in Textbooks. Length at maturity is 128 mm.  Max Length 227 in sealifebase.

### Spot
```{r echo=FALSE, message=FALSE, warning=FALSE}
spot <- lengths[grepl('xanthurus', scientific)]

spot <- spot %>% mutate(YOY =
                     case_when(length < 170 ~ "YOY", 
                               length >= 170 ~ "1+")
) #adding YOY threshold

h4<-ggplot(data=spot  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(length2, -length), text = paste("Week:", wk,"Length:", length, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(fill = length, color = length))+ ggtitle("YOY, Length by week") 

ggplotly(h4,tooltip = "text")

m4<-ggplot(data=spot  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(length2, -length), text = paste("Week:", wk,"Length:", length, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(fill = length, color = length))+ ggtitle("1+, Length by week") 

ggplotly(m4,tooltip = "text")
```
Background suggests spot are "No bigger than max lengths of 360 mm" with YOY max length around 170 - 210 mm. Outliers Removed > 360.


### Inland silverside
```{r echo=FALSE, message=FALSE, warning=FALSE}
inland <- lengths[grepl('beryllina', scientific)]

inland <- inland %>% mutate(YOY =
                     case_when(length < 60 ~ "YOY", 
                               length >= 60 ~ "1+")
) #adding YOY threshold

h5<-ggplot(data=inland  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(length2, -length), text = paste("Week:", wk,"Length:", length, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(fill = length, color = length))+ ggtitle("YOY, Length by week") 

ggplotly(h5,tooltip = "text")

m5<-ggplot(data=inland  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(length2, -length), text = paste("Week:", wk,"Length:", length, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(fill = length, color = length))+ ggtitle("1+, Length by week") 

ggplotly(m5,tooltip = "text")

```
Background suggests inland silversides are "No bigger than max lengths of 150 mm" with YOY max length around 40-60 mm. Outliers Removed >150.

### Striped bass
```{r echo=FALSE, message=FALSE, warning=FALSE}
bass <- lengths[grepl('saxatilis', scientific)]

bass <- bass %>% mutate(YOY =
                     case_when(length < 270 ~ "YOY", 
                               length >= 270 ~ "1+")
) #adding YOY threshold

h6<-ggplot(data=bass  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(length2, -length), text = paste("Week:", wk,"Length:", length, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(fill = length, color = length))+ ggtitle("YOY, Length by week") 

ggplotly(h6,tooltip = "text")

m6<-ggplot(data=bass  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(length2, -length), text = paste("Week:", wk,"Length:", length, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(fill = length, color = length))+ ggtitle("1+, Length by week") 

ggplotly(m6,tooltip = "text")

```
Background suggests striped bass are "No bigger than max lengths of 2000 mm" with YOY max length around 150-270 mm

### Bluefish
```{r echo=FALSE, message=FALSE, warning=FALSE}
blue <- lengths[grepl('saltatrix', scientific)]

blue <- blue %>% mutate(YOY =
                     case_when(length < 140 ~ "YOY", 
                               length >= 140 ~ "1+")
) #adding YOY threshold

h7<-ggplot(data=blue  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(length2, -length), text = paste("Week:", wk,"Length:", length, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(fill = length, color = length))+ ggtitle("YOY, Length by week") 

ggplotly(h7,tooltip = "text")

m7<-ggplot(data=blue  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(length2, -length), text = paste("Week:", wk,"Length:", length, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(fill = length, color = length))+ ggtitle("1+, Length by week") 

ggplotly(m7,tooltip = "text")
```
Background suggests bluefish are "No bigger than max lengths of 1300 mm" with YOY max length around 130-140 mm. Outliers Removed > 700 .

### Bay anchovy
```{r echo=FALSE, message=FALSE, warning=FALSE}
ancho <- lengths[grepl('mitchilli', scientific)]
outlierReplace(ancho, "length", which(ancho$length > 110), NA)  
ancho <- ancho %>% mutate(YOY =
                     case_when(length < 60 ~ "YOY", 
                               length >= 60 ~ "1+")
) #adding YOY threshold

h8<-ggplot(data=ancho  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(length2, -length), text = paste("Week:", wk,"Length:", length, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(fill = length, color = length))+ ggtitle("YOY, Length by week") 

ggplotly(h8,tooltip = "text")

m8<-ggplot(data=ancho  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(length2, -length), text = paste("Week:", wk,"Length:", length, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(fill = length, color = length))+ ggtitle("1+, Length by week") 

ggplotly(m8,tooltip = "text")
```
Background suggests bay anchovy are "No bigger than max lengths of 110 mm" with YOY max length around 20-60 mm. Outliers Removed > 110.



### Menhaden
```{r echo=FALSE, message=FALSE, warning=FALSE}
men <- lengths[grepl('brevoortia tyrannus', scientific)]

men <- men %>% mutate(YOY =
                     case_when(length < 170 ~ "YOY", 
                               length >= 170 ~ "1+")
) #adding YOY threshold

h9<-ggplot(data=men  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(length2, -length), text = paste("Week:", wk,"Length:", length, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(fill = length, color = length))+ ggtitle("YOY, Length by week") 

ggplotly(h9,tooltip = "text")

m9<-ggplot(data=men  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(length2, -length), text = paste("Week:", wk,"Length:", length, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(fill = length, color = length))+ ggtitle("1+, Length by week") 

ggplotly(m9,tooltip = "text")
```

Background suggests menhaden are "No bigger than max lengths of 500 mm" with YOY max length around 80-170 mm. 

### Gizzard shad
```{r echo=FALSE, message=FALSE, warning=FALSE}
shad <- lengths[grepl('dorosoma cepedianum', scientific)]

shad <- shad %>% mutate(YOY =
                     case_when(length < 180 ~ "YOY", 
                               length >= 180 ~ "1+")
) #adding YOY threshold

h10<-ggplot(data=shad  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(length2, -length), text = paste("Week:", wk,"Length:", length, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(fill = length, color = length))+ ggtitle("YOY, Length by week") 

ggplotly(h10,tooltip = "text")

m10<-ggplot(data=shad  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(length2, -length), text = paste("Week:", wk,"Length:", length, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(fill = length, color = length))+ ggtitle("1+, Length by week") 

ggplotly(m10,tooltip = "text")
```
Background suggests bay gizzard shad are "No bigger than max lengths of 570 mm" with YOY max length around 100-180 mm

### White perch
```{r echo=FALSE, message=FALSE, warning=FALSE}
perch <- lengths[grepl('morone americana', scientific)]

perch <- perch %>% mutate(YOY =
                     case_when(length < 93 ~ "YOY", 
                               length >= 93 ~ "1+")
) #adding YOY threshold

h11<-ggplot(data=perch  %>% filter(YOY == "YOY"), aes(x=wk, y=counts, order = reorder(length2, -length), text = paste("Week:", wk,"Length:", length, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(fill = length, color = length))+ ggtitle("YOY, Length by week") 

ggplotly(h11,tooltip = "text")

m11<-ggplot(data=perch  %>% filter(YOY == "1+"), aes(x=wk, y=counts, order = reorder(length2, -length), text = paste("Week:", wk,"Length:", length, "Year:", year), show.legend=T)) +
  geom_bar(stat="identity", aes(fill = length, color = length))+ ggtitle("1+, Length by week") 

ggplotly(m11,tooltip = "text")
```
Background suggests white perch are "No bigger than max lengths of 580 mm" with YOY max length around 100-250 mm
